\section{Conclusion and Future Work}

With the rapid development in the field of Internet and technology, IoT is changing our lives by making things smarter and easier than ever before. This technological improvement has made a positive approach in many fields that are based on a peer-to-peer structure by running on cheap and easily available hardware devices. We built a multimedia system that uses RTP on the RPi4. Our system receives the video stream from the attached camera node, which is encoded and decoded by using two video codecs (H.264 and MJPEG) in four frameworks (CVLC, FFmpeg, MJPG-Streamer, GStreamer) and sent over the network using an RTP. To view the video streamed from RPi, we use the web browser or media-player (VLC) on the receiving device. As our system is virtualized using Docker containers, it makes deployment easy on RPi. \par

By comparing all the frameworks with its respective codecs on RPi3 and RPi4 in terms of resource utilization (CPU, memory, network throughput) and video quality, we arrive at a conclusion that MJPG-Streamer delivers the best performance overall and it only supports the MJPEG codec as WebRTC requires H.264 in RPi4. Followed by is the GStreamer providing the best results in RPi4. And about RPi3, unfortunately in our project, we are unable to view the video stream from the RPi3 except for MJPG-Streamer, which affects the result. This leads to an uncertain situation to determine which multimedia framework is the best on RPi3 and difficult to conclude which RPi is the best. In our project, we realized Janus (WebRTC server) supports very few video codecs and multimedia frameworks, this is why we haven't used MJPEG codec with GStreamer. \par 

Also, we realized, ARM quad-core processor (RPi) does not fully support multimedia frameworks because of no built-in libraries and Graphics Processing Unit (GPU) chip. \par

While our prototype demonstrates the possibilities with current technology using cheap SBCs, future work may provide a more stable foundation in using various other multimedia frameworks for better video streaming quality and added new features.